---
title: "provincedata"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

## Province data
```{r}
library(dplyr)
data <- read.csv('/Users/HW/Provincedata/provincedata.csv')
head(data)
cor_data <- data[,names(data) %in% c('nowConfirm','confirm','dead','deadRate',
                                     'heal','healRate')]
```
- Question 1: What are top 10 provinces for nowConfirm in China?

```{r}
library(ggplot2)
unique(data$name)
dat <- data %>% select(name,nowConfirm) %>% arrange(desc(nowConfirm)) %>% slice(1:10) 
ggplot(data=dat,aes(x=name,y=nowConfirm)) + geom_bar(stat = 'identity')
```

- Question 2: What are the top 10 provinces for deadRate in China?

```{r}
library(ggplot2)
dat <- data %>% select(name,deadRate) %>% arrange(desc(deadRate)) %>% slice(1:10) 
ggplot(data=dat,aes(x=name,y=deadRate)) + geom_bar(stat = 'identity')
```

- Question 3: What are the top 10 provinces for heal in China?
```{r}
library(ggplot2)
dat <- data %>% select(name,heal) %>% arrange(desc(heal)) %>% slice(1:10) 
ggplot(data=dat,aes(x=name,y=heal)) + geom_bar(stat = 'identity')
```

- Question 4: Is there any corelation between dead and heal?
- Question 5: Is there any corelation between healRate and nowConfirm?

```{r}
library(corrplot)
cor(mtcars[1:5])
corrplot(cor(cor_data), method = "circle")
```

- Question 6: what is the distribution of (healRate/deadRate)?

```{r}
ggplot(data,aes(x=healRate))+geom_density() # left skewed
ggplot(data,aes(x=deadRate))+geom_density() # right skewed
```

- Question 7: Is there any relationship between (healRate) and (deadRate)?
```{r}
lm.model <- lm(healRate~deadRate,data=data)
summary(lm.model) 
ggplot(data,aes(x=healRate,y=deadRate))+geom_point()# no relationship
ggplot(data,aes(x=nowConfirm,y=deadRate))+geom_point() 
```


